---
title: "BrPoliCorpus: Brazilian Political Corpus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BrPoliCorpus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BrPoliCorpus)
```

by [Rodrigo Esteves de Lima-Lopes](mailto:rll307@unicamp.br) (Universidade Estadual de Campinas)

# Introduction
BrPoliCorpus is a corpus consisting of Brazilian official Brazilian documents. It can be used both as a R package or a set of CSV files freely downloadable here. This manual is dedicated exclusively for the R package basic usage. 

# Data

BrPoliCorpus consists of over 440 billions words. Such large amount of data could not be distributed through GitHub or any other package hosting services. Each time a data function is called, the package will try to download the data from UNICAMP's servers into your R environment. 

# Commands
Here some important commands that will help you out through the corpus:

`download_index()`

Creates six data frames in your environment:

1. IndexProgrammes:
  - Indexes all government proposals available.
2. IndexInauguralSpeeches: 
  - Indexes all Inaugural Speeches available.
3. IndexFloorPlenaries
  - Indexes all Floor Plenaries available.
4. IndexCPI
  - Indexes all Congress Committees of Inquiry available.
5. IndexCommittees
  - Indexes all Congress Committees (_not Inquiry_) available.
6. GeneralIndex
  - Indexes all commands available.

For example `download_Brasil_president_2014()` downloads the government proposals for the candidates of the Brazilian Presidency in 2014. A common usage would be:

```{r eval=FALSE, echo=TRUE}
Brasil_2024 <- download_Brasil_president_2014()
```

This creates a data frame with this part of the corpus. Please, refer to `GeneralIndex` for the whole set of commands. The other data frames mentioned above will bring you necessary details, such as the date and the nature of each dataset. 